Molecular dynamics simulation of synchronization in driven particles

### 2021-01-04 manuscript/manuscript_ajp_2020.tex
renamed and removed sections

\subsection{Synchronization in multi-particle systems}
\label{sec:sync}

@@

\subsection{Kinked system}
\label{sec:kink}	% You can label sections for reference
We confine $N$ particles to $N-1$ troughs to create a
local high density region.
$F^{DC}/F^{AC} = 1$ [CHECK!]

\section{Quasi-periodic substrate}
\label{sec:quasiperiod}	% You can label sections for reference

\section{Chaotic dynamics}
\label{sec:chaos}	% You can label sections for reference

@@

  Reasonable experimental values for
  a colloid are $D = 1 \mu m$ and $v \sim 1 \mu m /s$.
  Viscosity of water decreases with temperature
  from $1.3 \times 10^{-3} Pa s$ at $10^{\circ}C$ to 
  from $0.31 \times 10^{-3} Pa s$ at $90^{\circ}C$,
  making $\eta \sim 10^{-3} Pa s $.
  Likewise the density $\rho$ varies with temperature
  and $\rho \sim 10^3 kg/cm^3$ is a reasonable approximation.

>>>>

\section{Synchronization in multi-particle systems}
\label{sec:sync}

@@

\section{Kinked system}
\label{sec:kink}	% You can label sections for reference
We confine $N$ particles to $N-1$ troughs to create a
local high density region.
$F^{DC}/F^{AC} = 1$ [CHECK!]

%\section{Quasi-periodic substrate}
%\label{sec:quasiperiod}	% You can label sections for reference

%\section{Chaotic dynamics}
%\label{sec:chaos}	% You can label sections for reference

@@

  Reasonable experimental values for
  a colloid are $D = 1 \mu m$ and $v \sim 1 \mu m /s$.
  Viscosity of water decreases with temperature
  from $1.3 \times 10^{-3} Pa-s$ at $10^{\circ}C$ to 
  from $0.31 \times 10^{-3} Pa-s$ at $90^{\circ}C$,
  making $\eta \sim 10^{-3} Pa-s$,
  where 1 pascal $ = 1 Pa = 1 N/m^2$.
  Likewise the density $\rho$ varies with temperature
  and $\rho \sim 10^3 kg/cm^3$ is a reasonable approximation.
